This chapter introduces the concepts necessary to understanding the subject of this thesis -- implementing a learning agent using reinforcement learning.

In \emph{Chapter \ref{agents-intro}. Intelligent Agents} we aim to present the central pieces of the \textbf{agent-based approach} in artificial intelligence: agent and environment.
We explore the constituents of a learning agent and explain how we can reason about problems using the notion of task environment.

\emph{Chapter \ref{reinforcement-learning}. Reinforcement Learning} introduces key concepts in the field of RL. This chapter deals with \textbf{theoretical fundamentals} (Markov decision processes) and their application in solving problems in this paradigm.

In the same chapter, we present an array of \textbf{classical solution methods}, ranging from Monte Carlo (which simply applies statistical sampling to learn from an unknown environment) to more subtle methods such as temporal-difference (TD) learning.

In \emph{Chapter \ref{deep-rl}. Deep Reinforcement Learning}, we explain how to scale the classical solutions to solve larger (and more relevant) problems using \textbf{functional approximation}.
Deep RL represents an \textbf{active area of reasearch} and an extensive survey of the state-of-the-art would be out of the scope of this paper.
Instead, we cover a few tried-and-tested solution methods which had moderate success in their application.

\clearpage

\section{Intelligent Agents} \label{agents-intro}
\input{chapters/background/intelligent_agents.tex}

\section{Reinforcement Learning} \label{reinforcement-learning}
\input{chapters/background/rl.tex}

\section{Deep Reinforcement Learning} \label{deep-rl}
\input{chapters/background/deep-rl.tex}